Minimal Positive Influence of Helpline Efforts on Reduction of Homeless Death in Toronto

### 2024-03-12 paper/paper.qmd
found the error code chunk, it's the modelsummary chunk

library(tidyverse)
library(readr)
library(rstanarm)
library(knitr)
library(ggplot2)
```

@@

Our results are summarized in @tbl-total_coded_modelresults and
@tbl-referred_informed_modelresults.

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of homeless death count in relation to different helpline efforts"
#| tbl-subcap: "statistical significances are indicated by p < 0.1 *, p < 0.05 **, p < 0.01 ***, p < 0.001"
#| warning: false

modelsummary::modelsummary(
  list(
    "Total Coded Model" = total_coded_model, "Referred and Informed Model" = referred_informed_model
  ),
  statistic = "mad",
  stars = TRUE,
  fmt = 4
)
```

>>>>

library(tidyverse)
library(readr)
library(rstanarm)
library(knitr)
library(modelsummary)
library(ggplot2)
```

@@

Our results are summarized in @tbl-modelresults.

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of homeless death count in relation to different helpline efforts"
#| tbl-subcap: "statistical significances are indicated by p < 0.1 *, p < 0.05 **, p < 0.01 ***, p < 0.001"

modelsummary(
  list(
    "Total Coded Model" = total_coded_model, "Referred and Informed Model" = referred_informed_model
  ),
  statistic = "mad",
  stars = TRUE,
  fmt = 4,
  metrics = c("RMSE", "R2")
)
```
